The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-14 analysis/paper/paper.qmd
Remove duplicate references
Update script for loading packages

# Load packages ----
## Managing paths
library(here)

## Data manipulation and visualisation
library(tidyverse)

## Text processing and analysis
library(tidytext)
library(SnowballC)
library(tm)

## Working with spatial data
library(tidygeocoder)

>>>>

# Load packages ----
## List packages to be loaded
packages <- c(
  "here",                         # Managing paths
  "tidyverse",                    # Data manipulation and visualisation
  "tidytext", "SnowballC", "tm",  # Text processing and analysis
  "tidygeocoder"                  # Working with spatial data
)

## Load required packages, install them if needed
for (package in packages) {
  if (!require(package, character.only = TRUE)) {
    install.packages(package)
  }
  library(package, character.only = TRUE)
}
